---
title: "Modeling with Google Trends!"
author: "Emily Wilkins"
date: "3/28/2018"
output: html_document
---

This is just used to import the data and necessary packages. 
```{r, warning = F, error = F, message = F}
JOTR_data <- read.csv("~/Desktop/Trends_data.csv")
library(MASS)
library(rsq)
# View(JOTR_data)
```

## Joshua Tree!!!!!

#### Setting up 4 different models...
```{r}
## Just using that current month's google trends
JT_M1<-glm.nb(JOTR_all~Trends_JOTR, data=JOTR_data)
## Just using google trends at a lag of 1-month
JT_M2<-glm.nb(JOTR_all~TJ_1mo, data=JOTR_data)
## Just using google trends at a lag of 1-year
JT_M3<-glm.nb(JOTR_all~TJ_1yr, data=JOTR_data)
## All three!!!!
JT_M4<-glm.nb(JOTR_all~Trends_JOTR+TJ_1mo+TJ_1yr, data=JOTR_data)
```

#### A quick look at R-squareds

Before we begin, it's important to note that R-square for negative binomial regression does not exit and is not comparable to R^2 from OLS. 
This is a [pseudo R-squared](https://stats.idre.ucla.edu/other/mult-pkg/faq/general/faq-what-are-pseudo-r-squareds/), which is called Nagelkerke. It's similar to Cox and Snell, but I prefer it because it's on the same 0-1 scale, so more interpretable. 

Code:
```{r, results="hide"}
rsq(JT_M1, type = 'n') # Setting type to n means we're getting a corrected version of the likelihood-ratio-based measure, AKA NAGELKERKE!
rsq(JT_M2, type = 'n')
rsq(JT_M3, type = 'n')
rsq(JT_M4, type = 'n')
```

If we are interested in coefficients in the future, we can run this code to see all the details. For now, not needed. 

HOWEVER, all coefficents statistically significant at an alpha level of 0.01. 

```{r, eval = F}
summary(JT_M1)
summary(JT_M2)
summary(JT_M3)
summary(JT_M4)
```

***

## Death Valley!!!!

#### Setting up 4 different models...
```{r}
## Just using that current month's google trends
DV_M1<-glm.nb(DEVA_all~Trends_DEVA, data=JOTR_data)
## Just using google trends at a lag of 1-month
DV_M2<-glm.nb(DEVA_all~TD_1mo, data=JOTR_data)
## Just using google trends at a lag of 1-year
DV_M3<-glm.nb(DEVA_all~TD_1yr, data=JOTR_data)
## All three!!!!
DV_M4<-glm.nb(DEVA_all~Trends_DEVA+TD_1mo+TD_1yr, data=JOTR_data)
```

#### A quick look at R-squareds

Same deal, this is Nagelkerke, our fun pseudo-R-squared. 

Code:
```{r results="hide"}
rsq(DV_M1, type = 'n') # Setting type to n means we're getting a corrected version of the likelihood-ratio-based measure, AKA NAGELKERKE!
rsq(DV_M2, type = 'n')
rsq(DV_M3, type = 'n')
rsq(DV_M4, type = 'n')
```

If we are interested in coefficients in the future, we can run this code to see all the details. For now, not needed. 
HOWEVER, NONE OF THE COEFFICIENTS ARE STATISTICALLY SIG AT 0.05. 

```{r eval = F}
summary(DV_M1)
summary(DV_M2)
summary(DV_M3)
summary(DV_M4)
```

