---
title: "Model Selection and Creation"
author: "Matt Clark"
date: "May 15, 2018"
output:
  word_document: default
  html_document: default
---
## Load all required packages

Note: rstan and rstanarm require a c++ compiler to run 

[Download the C++ compiler here](https://github.com/stan-dev/rstan/wiki/Installing-RStan-on-Windows)


```{r}
library(Metrics)
library(readr)
Data <- read_csv("~/ParkBreak/Seasonal.csv")
View(Data)
library(rethinking)
library(shiny)
library(rstanarm)
library(rstan)
library(MASS)
library(ggplot2)
library(dplyr)
library(tidyr)
```

First, we will create frequentist models to check for significance and do leave-one-out cross validation (LOOCV) of our models. 

The first step in model creation is to standardize all of our variables so that the slopes are comparable.

```{r}
stdize<-function(x) {return((x-mean(x)/(2*sd(x))))}
Data$stdcci<-stdize(Data$CCIStag)
Data$stdgoog<-stdize(Data$GoogStag)
```

Now create the different models
Note: only the significant variables are displayed here...this is to save you from running the 50+ models that were required for parameter elimination. 

```{r}
M1<-glm.nb(SeasVis~stdcci,data=Data)
M2<-glm.nb(SeasVis~stdgoog,data=Data)
M3<-glm.nb(SeasVis~Season,data=Data)
M4<-glm.nb(SeasVis~stdcci+stdgoog,data=Data)
M5<-glm.nb(SeasVis~stdcci+Season,data=Data)
M6<-glm.nb(SeasVis~stdgoog+Season,data=Data)
M7<-glm.nb(SeasVis~stdgoog+Season+stdcci,data=Data)
M8<-glm(SeasVis~stdgoog+Season+stdcci,family="poisson",data=Data)
```

Let's run the LOOCV for the negative binomial and Poisson distributions

```{r}
leftout<-rep(NA,times=length(Data$SeasVis))
for(i in 1:length(Data$SeasVis)){
  sub_dat<-Data[-i,]
  m_sub<-glm.nb(SeasVis~stdcci+stdgoog+Season,data=Data)
  leftout[i]=predict(m_sub,newdat=Data[i,]) 
}

R2 <- function (x, y) cor(x, y) ^ 2
R2mod<-R2(exp(leftout),Data$SeasVis)
library('Metrics')
rmsemod<-rmse(leftout,Data$SeasVis)
R2mod
rmsemod

leftout<-rep(NA,times=length(Data$SeasVis))
for(i in 1:length(Data$SeasVis)){
  sub_dat<-Data[-i,]
  m_sub<-glm(SeasVis~stdcci+stdgoog+Season,family="poisson",data=Data)
  leftout[i]=predict(m_sub,newdat=Data[i,]) 
}

R2mod<-R2(exp(leftout),Data$SeasVis)
rmsemod<-rmse(leftout,Data$SeasVis)
R2mod
rmsemod
```

Cool, now that we know that the negative binomial model affords us the greatest out of sample predictive power,
let's run this model in a Bayesian context.

```{r}
fcmod<-stan_glm.nb(SeasVis~stdgoog+Season+stdcci,data=Data)
```

Great, now we have our Bayesian model, lets examine the posterior distributions and check out some plots.

```{r}
bayesplot::color_scheme_set("brightblue")
plot(fcmod, "areas",prob = 0.5, prob_outer = 0.9)

plot_title <- ggplot2::ggtitle("Posterior Distributions")
plot(fcmod, "hist") + plot_title

plot(fcmod, "dens_overlay", pars = "(Intercept)"
) + plot_title
```

These ^^ are useful, we can see that out chains are converging and out parameters look significant, lets look at the posterior distributions in a better way though.

```{r}
sam<-as.matrix(fcmod)
sam<-as.data.frame(sam)


sam <- sam %>% gather(value, sam[1:8,])

colnames(sam)[1] <- "Parameter"

colnames(sam)[2]<-"Estimate"

sam<-filter(sam, sam$Parameter!="(Intercept)")
sam<-filter(sam, sam$Parameter!="reciprocal_dispersion")

library(ggjoy)
ggplot(sam, aes(x=Estimate, y=Parameter, height=..density..)) +
  geom_vline(xintercept = 0, col = "grey70") +
  geom_density_ridges2(col = "grey70", fill = "royalblue", scale = 2.4) +
  ggtitle("Parameter Estimates") +
  theme(plot.title = element_text(color="black", size=24, face="bold"))+
  theme(axis.title.x = element_text(size=20,face="bold"))+
  theme(axis.title.y  = element_text(size=20,face="bold"))+
  theme(axis.text = element_text(size=18))+
  theme(axis.text  = element_text(size=18))

```

Cool, now lets look at our R^2 from our LOOCV and look at our predicted vs observed values over time.

We need to make a LOOCV data set for overnight visitation first
```{r}
fcmodON<-glm.nb(Overnight~stdgoog+Season+stdcci,data=Data)
leftout2<-rep(NA,times=length(Data$SeasVis))
for(i in 1:length(Data$SeasVis)){
  sub_dat<-Data[-i,]
  m_sub<-glm.nb(Overnight~stdcci+stdgoog+Season,data=Data)
  leftout2[i]=predict(m_sub,newdat=Data[i,]) 
}

R2mod2<-R2(exp(leftout2),Data$Overnight)
```
Note: if your "leftout" is still set to a Poisson distribution, so back and set it to negative binomial
```{r}

par(mfrow=c(1,1))

plot(exp(leftout)~Data$Year,col="red", cex=2,pch=17, ylab="Total Visitation",xlab="Year",
     main="Predicted vs Observed Total Visitation by Season")
legend("topleft", pch=c(17,16), col=c("red", "blue"), c("Predicted", "Observed"))
points(SeasVis~Year,data=Data,cex=2, pch=16, col="blue")

plot(exp(leftout2)~Data$Year,col="red", cex=2,pch=17, ylab="Overnight Visitation",xlab="Year",
     main="Predicted vs Observed Overnight Visitation by Season")
legend("topleft", pch=c(17,16), col=c("red", "blue"), c("Predicted", "Observed"))
points(Overnight~Year,data=Data,cex=2, pch=16, col="blue")




plot(leftout,log(Data$SeasVis),pch=16,cex=2,main="Leave-One-Out Cross Validation: Predicted vs Observed Total Visitation",
     xlab="Log of Predicted Total Visitation",ylab="Log of Observed Total Visitation")
abline(lm(leftout~log(Data$SeasVis)),col="red",lwd=2)
legend("topleft", bty="n", legend=paste("R2 =", format(R2mod, digits=4)))

plot(leftout2,log(Data$Overnight),pch=16,cex=2,main="Leave-One-Out Cross Validation: Predicted vs Observed Overnight Visitation",
     xlab="Log of Predicted Overnight Visitation",ylab="Log of Observed OvernightVisitation")
abline(lm(leftout2~log(Data$Overnight)),col="red",lwd=2)
legend("topleft", bty="n", legend=paste("R2 =", format(R2mod2, digits=4)))
```

Last thing we will do is see how many of our data points fall within the 50% credibility interval that we use for the forecasting app. The first example is Total visitation, the second is Overnight visitation

```{r}
n1<-25
n2<-75

fcmod<-stan_glm.nb(SeasVis~GoogStag+CCIStag+Season,data=Data)
leftout<-rep(NA,times=length(Data$SeasVis))
for(i in 1:length(Data$SeasVis)){
  df <- data.frame(CCIStag=Data$CCIStag[i],
                   GoogStag=Data$GoogStag[i],
                   Season=Data$Season[i])
  mod<-(posterior_predict(
    fcmod,df,draws=4000))
  upbound<-min(mod[mod > quantile(mod,prob=1-n1/100),])
  lwrbound<-max(mod[mod < quantile(mod,prob=1-n2/100),])
  inside<-sum(Data$SeasVis[i]>lwrbound & Data$SeasVis[i] < upbound)
  
  leftout[i]= inside
  
}
totinside<-sum(leftout)
percinside<-totinside/39
percinside

fcmodON<-stan_glm.nb(Overnight~GoogStag+Season+CCIStag,data=Data)
leftout<-rep(NA,times=length(Data$SeasVis))
for(i in 1:length(Data$SeasVis)){
  df <- data.frame(CCIStag=Data$CCIStag[i],
                   GoogStag=Data$GoogStag[i],
                   Season=Data$Season[i])
  mod<-(posterior_predict(
    fcmodON,df,draws=4000))
  upbound<-min(mod[mod > quantile(mod,prob=1-n1/100),])
  lwrbound<-max(mod[mod < quantile(mod,prob=1-n2/100),])
  inside<-sum(Data$Overnight[i]>lwrbound & Data$Overnight[i] < upbound)
  
  leftout[i]= inside
  
}
totinside<-sum(leftout)
percinside<-totinside/39
percinside
```






















